Normalized expressions

### 2021-03-03 analysis/normalized.Rmd
Percentages

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package), n_operations = mean(n_op, na.rm=TRUE), prop_envir = sum(!is.na(envir)) / n())

@@

```{r}
widespread_topcall <- E_cano %>%
  group_by(topcall) %>%
  summarize(n_call_sites = n_distinct(src_ref)) %>% 
  arrange(desc(n_call_sites))
```

@@

There are `r nb_fundef_callsites` call sites with function definitions.

@@

There are `r nb_modelf_call_sites` call sites with `mode.frame`.

@@

`r nb_mf_match.call` call sites out of `model.frame` `r nb_modelf_call_sites` call sites use the `match.call` pattern.

@@

There are `r nb_assigns_call_sites` call sites with assignments.

@@

There are `r nb_a_env_call_sites` call sites where `envir` is non-trivial, with an assignment.

@@

There are `r nb_m.c_call_sites` call sites using the `match.call`pattern.

@@

it amounts for `r nb_stat_call_sites` call sites.

@@

It happens for `r nb_m_n_top_call_sites` call sites.

@@

There are `r nb_blocks_call_sites` such call sites.

@@

It happens in `r nb_pre_post_call_sites` call sites so most of the call sites with blocks.

@@

There are `r nb_plotting_call_sites` plotting call sites.

@@

This already amounts to `r nb_parse_plot_call_sites` call sites.

@@

It happens in `r nb_infix_call_sites` call sites.

@@

```{r}
poly %>% filter(n_exprs > 1) %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  datatable()
```

>>>>

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = round(100 * sum(!is.na(envir)) / n(), 2))

@@

```{r}
widespread_topcall <- E_cano %>%
  group_by(topcall) %>%
  summarize(n_call_sites = n_distinct(src_ref), percent = round(ratio(n_call_sites, nb_call_sites), 2)) %>% 
  arrange(desc(n_call_sites))
```

@@

There are `r nb_fundef_callsites` call sites with function definitions, i.e. `r ratio(nb_fundef_callsites, nb_call_sites)` %.

@@

There are `r nb_modelf_call_sites` call sites with `mode.frame`, i.e. `r ratio(nb_modelf_call_sites, nb_call_sites)`%.

@@

`r nb_mf_match.call` call sites out of `model.frame` `r nb_modelf_call_sites` call sites use the `match.call` pattern, i.e. `r ratio(nb_mf_match.call, nb_modelf_call_sites)`%.

@@

There are `r nb_assigns_call_sites` call sites with assignments, i.e. `r ratio(nb_assigns_call_sites, nb_call_sites)`%.

@@

There are `r nb_a_env_call_sites` call sites where `envir` is non-trivial, with an assignment, i.e. `r ratio(nb_a_env_call_sites, nb_assigns_call_sites)`% of the call sites with assignments.

@@

There are `r nb_m.c_call_sites` call sites using the `match.call`pattern, i.e. `r ratio(nb_m.c_call_sites, nb_call_sites)`%.

@@

it amounts for `r nb_stat_call_sites` call sites, i.e `r ratio(nb_stat_call_sites, nb_call_sites)`%.

@@

It happens for `r nb_m_n_top_call_sites` call sites, i.e. `r ratio(nb_m_n_top_call_sites, nb_call_sites)`%.

@@

There are `r nb_blocks_call_sites` such call sites, i.e. `r ratio(nb_blocks_call_sites, nb_call_sites)`%.

@@

It happens in `r nb_pre_post_call_sites` call sites so most of the call sites with blocks (`r ratio(nb_pre_post_call_sites, nb_blocks_call_sites)`%).

@@

There are `r nb_plotting_call_sites` plotting call sites, i.e. `r ratio(nb_plotting_call_sites, nb_call_sites)`%.

@@

This already amounts to `r nb_parse_plot_call_sites` call sites, i.e. `r ratio(nb_parse_plot_call_sites, nb_plotting_call_sites)`% of the plotting call sites.

@@

It happens in `r nb_infix_call_sites` call sites, i.e. `r ratio(nb_infix_call_sites, nb_call_sites)`%.

@@

```{r}
poly %>% filter(n_exprs > 1) %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  mutate(percent = round(100 * n / nb_call_sites, 2)) %>% 
  datatable()
```
